---
title: "Lab001 Geviz"
author: "Antonio Morsette"
date: "2022-10-27"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    highlight: default
editor_options: 
  chunk_output_type: console
---
# Getting Set Up
### Load the required packages
```{r}
library(ggplot2)
library(sf)
library(tidyverse)
library(dplyr)
library(ggspatial)
library(viridis)
library(tmap)
```

### Load Data
We will load the data containing identified bird locations  
```{r}
bird <- st_read("F:/Grad School/01-Courses/2-1 Grad Year/EAS 648 - Advanced_Geoviz/Lab/01/Bird/bird.shp")
study_area <- st_read("F:/Grad School/01-Courses/2-1 Grad Year/EAS 648 - Advanced_Geoviz/Lab/01/Bird/study_area.shp")
```

### Now let's use the package SF to change the projection
Because I have a z value in the points, st_transform(bird,32717) was not working. I would get:
*OGR: Not enough data 
*Error in CPL_transform(x, crs, aoi, pipeline, reverse, desired_accuracy,  : 
*OGR error
I found a I had to remove the z value using st_zm.

I'm reprojecting into WGS 84 / UTM zone 17S. Study area is already in WGS 84 / UTM zone 17S.

```{r}
bird <- st_transform(st_zm(bird),crs = 32717)
```

# Map the Data
To be able to plot the bird data in the map, I converted the data to a sf. If I didn't do this, I would get an error every time I try to plot it.

```{r}
bird <- st_as_sf(bird, coords = c("Longitude", "Latitude"))

bird %>% ggplot() +
  geom_sf(data = study_area,
          fill = "light blue", alpha = .2) +
  theme_bw() +
  geom_sf() +
  theme_bw()
```

# Interactive Maps

### Interactive Map 1
I am creating an interactive map of my study area.
This map is showing what I'd like it to show, but the not the colors. 
```{r}
tmap_mode("view")
bird %>% tm_shape() +
  tm_sf(data = study_area, 
        col = "blue", alpha = .2) +
  tm_shape(bird, projection = c("Longitude", "Latitude")) +
  tm_symbols()
```

### Interactive Map 2
Here I am working to get the colors the way I like them and to add a legend. I found a [video](https://www.youtube.com/watch?v=WsbkVkBLkdQ) to help me. 

```{r}
tm_shape(study_area) +
  tm_polygons(id = "Nombre", 
              col = "blue", 
              alpha = .2) +
  tm_shape(bird) +
  tm_bubbles(id = "Point_Name",
             size = 0.000025,
             col = "Total__",
             popup.vars = TRUE)
```

### Interactive Map 3
The colors are based on the total bird calls heard at each site, as opposed the number identified.
```{r}
tm_shape(study_area) +
  tm_polygons(id = "Nombre", 
              col = "blue", 
              alpha = .2) +
  tm_shape(bird) +
  tm_bubbles(id = "Point_Name",
             size = 0.000025,
             col = "Bird_Calls",
             popup.vars = TRUE)
```
The colors vary more in this map.

## Final Interactive Map
This map shows the difference between Maps 2 and 3, together. 
```{r}
tmap_mode("view")
tm_shape(study_area) +
  tm_polygons(id = "Nombre", 
              col = "blue", 
              alpha = .2) +
  tm_shape(bird) +
  tm_bubbles(id = "Point_Name",
             size = 0.000025,
             col = c("Bird_Calls","Total__"),
             popup.vars = TRUE)
```


# Plot the Data

First, we're going to see how many observations are at each property
```{r}
properties <- bird %>% 
  group_by(Property) %>% 
  tally()

head(properties)

####grouped by total bird calls heard

properties2<- bird %>% 
  group_by(Property) %>% 
  tally(Bird_Calls)
head(properties2)


####grouped by total bird calls identified
properties3<- bird %>% 
  group_by(Property) %>% 
  tally(Total__)
head(properties3)
```

### Plot Birds Identified
Next we will be plotting our data to see the means of our different plots. We are plotting how many birds were identified at each property. 
```{r}
bird %>%
  group_by('Property') %>%
  ggplot(aes(x=Property, y=Total__)) + 
  geom_boxplot()

```

More analysis will need to be done to  see the differences in the different plots. There are two types of plots, mono-culture and non-mono-culture. As it stands now, there is very little difference in the data.

### Plot Total Bird Calls
We're going to plot the total bird calls heard at each site, as opposed the number identified. 
```{r}
bird %>%
  group_by('Property') %>%
  ggplot(aes(x=Property, y=Bird_Calls)) + 
  geom_boxplot()
```

The plots look much different here. Again, more analysis is needed for the different plots, but there does seem to be a bigger difference in the means here. 



